The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-11-28 razzo-hypotheses.tex
Hypothesis (of no biological relevance) regarding candidate models

$\mathcal{H}_8$: RJCB expects that the JC69 and strict clock 
candidate models, the close

>>>>

$\mathcal{H}_8$: RJCB expects that for settings without extinctions,
the candidate model with JC69, strict and Yule will come up as the best
model most, as that model is the generative model, where the HKY, strict, BD
will be seleted least, as both its site and tree model are needlessly complex.
For settings with extinctions, RJCB predict HKY, strict and Yule will come up 
as the worst model mostly, as it uses both an incorrect site model and incorrect
tree model. \richel{I would enjoy a hypothesis of actual biological relevance for the
candidate models. If we cannot devise one, I suggest to remove the
use of candidate models}
